---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# nccosseasim

<!-- badges: start -->
[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](https://www.repostatus.org/badges/latest/active.svg)](https://www.repostatus.org/#active)
<!-- badges: end -->

## Overview

The `nccosseasim` package provides a suite of functions for running simulations to inform sampling design decisions within the NOAA National Centers for Coastal Ocean Science (NCCOS) Seascape Ecology and Analytics (SEA) branch. It includes tools for simulating compositional data, analyzing simulation results, and visualizing outcomes to support sampling design and data collection decisions.

## Features

* Simulate compositional data for ecological analyses
* Run simulations with different parameterizations 
* Compare metrics across simulation scenarios
* Fit Dirichlet models to compositional data
* Visualize simulation results with customizable plotting functions

## Installation

You can install the development version of nccosseasim from GitHub:

```{r, message = FALSE}
# install.packages("pak")
pak::pkg_install("jeffery-leirness/nccosseasim")
```

## Usage

```{r}
library(nccosseasim)

# Example code will go here
# simulate_compositional_data()
# run_simulation_compositional_data()
# plot_compositional_data()
```

## Getting help

If you encounter a bug, please file an issue with a minimal reproducible example on GitHub.

## Disclaimer

This repository is a scientific product and is not official communication of the National Oceanic and Atmospheric Administration, or the United States Department of Commerce. All NOAA GitHub project code is provided on an 'as is' basis and the user assumes responsibility for its use. Any claims against the Department of Commerce or Department of Commerce bureaus stemming from the use of this GitHub project will be governed by all applicable Federal law. Any reference to specific commercial products, processes, or services by service mark, trademark, manufacturer, or otherwise, does not constitute or imply their endorsement, recommendation or favoring by the Department of Commerce. The Department of Commerce seal and logo, or the seal and logo of a DOC bureau, shall not be used in any manner to imply endorsement of any commercial product or activity by DOC or the United States Government.

## License

This software is in the public domain in the United States and is released internationally under a royalty-free, nonexclusive license. See the [LICENSE](LICENSE) file for full details.
